---
title: "Assignment 3: Data set Pathway and Network Analysis"
author: "Koji Wong"
date: "04/01/2025"
bibliography: "A3_bib.bib"
output:
    html_document:
        toc: true
        toc_float: true
        fig_caption: yes
        number_sections: true
        theme: cosmo
        highlight: tango
        code_folding: show
        df_print: paged
        self_contained: yes
nocite: '@*'
---

# Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "figures/")

# install dependencies
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

if (!require("tools", quietly = TRUE))
  install.packages("tools")

if (!requireNamespace("edgeR", quietly = TRUE))
  BiocManager::install("edgeR")

if (!requireNamespace("limma", quietly = TRUE))
  BiocManager::install("limma")

if (!requireNamespace("pheatmap", quietly = TRUE))
  BiocManager::install("pheatmap")

if (!requireNamespace("ggplot2", quietly = TRUE))
  BiocManager::install("ggplot2")

if (!requireNamespace("dplyr", quietly = TRUE))
  BiocManager::install("dplyr")

library(dplyr)
library(ggplot2)
```

```{r eval = TRUE, message=TRUE}
print(getwd())
```

In our last assignment, we created a ranked list of genes for genesets with upregulated genes and downregulated genes. We have uploaded them to github and load them in below.
```{r eval=TRUE, message=TRUE}
print(getwd())
# Getting the ranked gene sets from Assignment 2
destfile = "precomputed/upreg_genes_gost.rds"
if (!file.exists(destfile)) {
  download.file(
    url = "https://github.com/bcb420-2025/Koji_Wong/raw/refs/heads/main/A3_KojiWong/precomputed/upreg_genes_gost.rds",
    destfile = destfile
  )
}
# Load in the normalized count matrix from our rds object file
upreg_genes_gost <- readRDS(destfile)

destfile = "precomputed/downreg_genes_gost.rds"
if (!file.exists(destfile)) {
  download.file(
    url = "https://github.com/bcb420-2025/Koji_Wong/raw/refs/heads/main/A3_KojiWong/precomputed/downreg_genes_gost.rds",
    destfile = destfile
  )
}
# Load in the normalized count matrix from our rds object file
downreg_genes_gost <- readRDS(destfile)
```

#Links to an external site.Non-thresholded Gene set Enrichment Analysis

## Conduct non-thresholded gene set enrichment analysis using the ranked set of genes from Assignment #2.

> Q1. What method did you use? What genesets did you use? Make sure to specify versions and cite your methods.
Summarize your enrichment results.



> Q2. How do these results compare to the results from the thresholded analysis in Assignment #2. Compare qualitatively. Is this a straight forward comparison? Why or why not?
```
```